Scheduling and Amortization for MPC

### 2022-01-02 paper_SIMD.tex
Add note about pseudo-phi node placement
Add note to paper about biometric example

\begin{itemize}
\item same-level forward $X\rightarrow Y$ where $X$ and $Y$ are in the same loop nest $i_1,i_2,...i_k$. E.g., $\texttt{d} = \mathit{SUM}(\texttt{S}[i,j], \texttt{C}[j])$ to $\texttt{p} = \mathit{MUL}(\texttt{d},\texttt{d})$ in Biometric is a same-level edge. A $\phi$ node can be a source of a same-level forward edge but not a target. 
\item outer-to-inner forward $X\rightarrow Y$ where $X$ is in an outer loop nest, $i_1,i_2,...i_j$, and $Y$ is in an inner one, $i_1,i_2,...i_j,...,i_k$. A $\phi$-node can be a source or a target of an outer-to-inner forward edge. 
\item inner-to-outer forward $X\rightarrow Y$ where $X$ is a $phi$-node in an inner loop nest, $i_1,i_2,...i_k,i_{k+1}$, and $Y$ is in the enclosing loop nest $i_1,i_2,...i_k$. E.g. $\texttt{sum}_0 = \phi(\texttt{sum}_1, 0)$ to $\texttt{c} = \mathit{CMP}(\texttt{sum}_0,\texttt{min}_0)$ is an inner-to-outer forward edge. Note that the source is \emph{always} a $\phi$-node in the immediately enclosing loop. The interpretation of this edge is that the use node $Y$ uses the definition made in the last iteration of the inner loop. 
\item same-level back-edge $X\rightarrow Y$. $Y$ is a phi-node in the header of the loop and $X$ is a definition of the variable in the loop body. E.g., $\texttt{min}_1 = \mathit{MUX}(\texttt{c},\texttt{sum}_1,\texttt{min}_1)$ to $\texttt{min}_0 = \phi(\texttt{min}_1, 10000)$ in Biometric is a same-level back-edge. 
\item inner-to-outer back-edge $X\rightarrow Y$: $X$ and $Y$ are both $\phi$-nodes for some variable. The source $X$ is in a loop nested into $Y$'s loop (not necessarily immediately).

@@

>>>>

\begin{itemize}
\item same-level forward $X\rightarrow Y$ where $X$ and $Y$ are in the same loop nest $i_1,i_2,...i_k$. E.g., $\texttt{d} = \mathit{SUM}(\texttt{S}[i,j], \texttt{C}[j])$ to $\texttt{p} = \mathit{MUL}(\texttt{d},\texttt{d})$ in Biometric is a same-level edge. A $\phi$ node can be a source of a same-level forward edge but not a target.
\item outer-to-inner forward $X\rightarrow Y$ where $X$ is in an outer loop nest, $i_1,i_2,...i_j$, and $Y$ is in an inner one, $i_1,i_2,...i_j,...,i_k$. A $\phi$-node can be a source or a target of an outer-to-inner forward edge.
\item inner-to-outer forward $X\rightarrow Y$ where $X$ is a $phi$-node in an inner loop nest, $i_1,i_2,...i_k,i_{k+1}$, and $Y$ is in the enclosing loop nest $i_1,i_2,...i_k$. E.g. $\texttt{sum}_0 = \phi(\texttt{sum}_1, 0)$ to $\texttt{c} = \mathit{CMP}(\texttt{sum}_0,\texttt{min}_0)$ is an inner-to-outer forward edge. Note that the source is \emph{always} a $\phi$-node in the immediately enclosing loop. The interpretation of this edge is that the use node $Y$ uses the definition made in the last iteration of the inner loop.
\ben{The current representation of pseudo $\phi$-nodes shows them attached to the loop header (i.e. in the loop).  We may want to clarify that they are also evaluated at the loop's termination.}
\item same-level back-edge $X\rightarrow Y$. $Y$ is a phi-node in the header of the loop and $X$ is a definition of the variable in the loop body. E.g., $\texttt{min}_1 = \mathit{MUX}(\texttt{c},\texttt{sum}_1,\texttt{min}_1)$ to $\texttt{min}_0 = \phi(\texttt{min}_1, 10000)$ in Biometric is a same-level back-edge.
\item inner-to-outer back-edge $X\rightarrow Y$: $X$ and $Y$ are both $\phi$-nodes for some variable. The source $X$ is in a loop nested into $Y$'s loop (not necessarily immediately).

@@

\ben{The above code implicitly stores the final values of min\_0 and index\_0 in their last indices, but there is no primitive like drop\_dim to make it clear.  This will have to be added in the SSA code generation (though it might not be necessary to include in the paper?).  It also is pretty wishy-washy about the size and layout of each vector (again more of an implementation issue), but maybe we should have a different syntax for array accesses for read/write (e.g. the ADD\_SIMD steps) vs the array definitions (e.g. the SUB\_SIMD and raise/drop\_dim statements)}
